---
title: "Activin_TCGA"
output: html_document
date: "2022-10-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("recount3")
ovarian_recount3 <- recount3::create_rse_manual(
  project = "OV",
  project_home = "data_sources/tcga",
  organism = "human",
  annotation = "gencode_v26",
  type = "gene"
)
```

```{r}
ovarian_counts <- ovarian_recount3@assays@data@listData$raw_counts
write.csv(ovarian_counts, "~/Desktop/rawcounts.csv")
```

```{r}
#necessary meta data 
tcga_barcodes <- ovarian_recount3@colData@listData[["tcga.tcga_barcode"]]
project_names <- ovarian_recount3@colData@listData[["tcga.gdc_cases.project.name"]]
write.csv(tcga_barcodes, "~/Desktop/barcodes.csv")
write.csv(project_names, "~/Desktop/project_names.csv")
```

```{r}
case_id <- ovarian_recount3@colData@listData[["tcga.gdc_cases.case_id"]]
write.csv(case_id, "~/Desktop/case_id.csv")
```


before this make the meta information from TCGA's website as well as the information from above 

```{r message= FALSE, warning= FALSE, echo=FALSE}
library(tximport)
library(GenomicFeatures)
library(TxDb.Hsapiens.UCSC.hg19.knownGene)
library(DESeq2)
library(tibble)
library(ggplot2)
```

```{r message= FALSE, warning= FALSE, echo=FALSE}
sample_meta_data <- read.csv("~/Desktop/Elizabeth_Figures/TCGA_meta.csv")
sampleNames <- sample_meta_data$From_Original_Order
figo_stage <- sample_meta_data$figo_stage

sampleTable <- data.frame(sampleName = sampleNames,
                          condition = figo_stage)
sampleTable$condition <- factor(sampleTable$condition)
dds <- DESeqDataSetFromMatrix(ovarian_counts, sampleTable, ~condition)
```


```{r message= FALSE, warning= FALSE, echo=FALSE}
dds <- estimateSizeFactors(dds)
idx <- rowSums(counts(dds, normalized=TRUE) >= 5 ) >= 3
dds <- dds[idx,]
```


```{r message= FALSE, warning= FALSE, echo=FALSE}
library(BiocParallel)
dds <- DESeq(dds, quiet=TRUE, parallel=TRUE, BPPARAM=MulticoreParam(3))
```


```{r message= FALSE, warning= FALSE, echo=FALSE}
res <- results(dds)
```

```{r}
res
```

```{r}
resOrdered <- res[order(res$pvalue),]
summary(res)
```

```{r}
res05 <- results(dds, alpha=0.05)
summary(res05)
```

```{r}
plotMA(res, ylim= c(-2,2))
```
#Analysis of Genes of Interest by Stage 
#### INHA 
```{r}
counts <- counts(dds['ENSG00000123999.4', ], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_jitter(width = 0.1) + aes(color= group) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") 
q <- q + labs(x = "Stage", y = "Normalized Counts ", title = "Expression of INHBA")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/INHA.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_INHA.csv")
```

#### INHBA
```{r}
counts <- counts(dds['ENSG00000122641.10' , ], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_jitter(width = 0.1) + aes(color= group) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") 
q <- q + labs(x = "Stage", y = "Normalized Counts ", title = "Expression of INHBA")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/INHBA.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_INHBA.csv")
```

#### ACVR2A
```{r}
counts <- counts(dds['ENSG00000121989.14',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_jitter(width = 0.1) + aes(color= group) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") 
q <- q + labs(x = "Stage", y = "Normalized Counts ", title = "Expression of ACVR2A")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/ACVR2A.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_ACVR2A.csv")
```

#### ACVR2B
```{r}
counts <- counts(dds['ENSG00000114739.13',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_jitter(width = 0.1) + aes(color= group) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") 
q <- q + labs(x = "Stage", y = "Normalized Counts ", title = "Expression of ACVR2B")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/ACVR2B.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_ACVR2B.csv")
```

#### FOXP3
```{r}
counts <- counts(dds['ENSG00000049768.14',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_jitter(width = 0.1) + aes(color= group) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") 
q <- q + labs(x = "Stage", y = "Normalized Counts ", title = "Expression of FOXP3")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/FOXP3.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_FOXP3.csv")
```

#### INHBB
```{r}
counts <- counts(dds['ENSG00000163083.5',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_jitter(width = 0.1) + aes(color= group) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") 
q <- q + labs(x = "Stage", y = "Normalized Counts ", title = "Expression of INHBB")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/INHBB.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_INHBB.csv")
```

#### ACVR1B
```{r}
counts <- counts(dds['ENSG00000135503.12',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_jitter(width = 0.1) + aes(color= group) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") 
q <- q + labs(x = "Stage", y = "Normalized Counts ", title = "Expression of ACVR1B")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/ACVR1B.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_ACVR1B.csv")
```

#### ACVR1C
```{r}
counts <- counts(dds['ENSG00000123612.15',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_jitter(width = 0.1) + aes(color= group) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") 
q <- q + labs(x = "Stage", y = "Normalized Counts ", title = "Expression of ACVR1C")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/ACVR1C.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_ACVR1C.csv")
```

#### CD8A
```{r}
counts <- counts(dds['ENSG00000153563.15',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_jitter(width = 0.1) + aes(color= group) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") 
q <- q + labs(x = "Stage", y = "Normalized Counts ", title = "Expression of CD8A")
q
```
```{r}
ggsave("~/Desktop/Elizabeth_Figures/CD8A.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/countsCD8A.csv")
```

#### CD3G
```{r}
counts <- counts(dds['ENSG00000160654.9',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_jitter(width = 0.1) + aes(color= group) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") 
q <- q + labs(x = "Stage", y = "Normalized Counts ", title = "Expression of CD3G")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/CD3G.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_CD3G.csv")
```

#### MMP3 
```{r}
counts <- counts(dds['ENSG00000149968.11',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_jitter(width = 0.1) + aes(color= group) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") 
q <- q + labs(x = "Stage", y = "Normalized Counts ", title = "Expression of MMP3")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/MMP3.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_MMP3.csv")
```

#### MMP13
```{r}
counts <- counts(dds['ENSG00000137745.11',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_jitter(width = 0.1) + aes(color= group) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") 
q <- q + labs(x = "Stage", y = "Normalized Counts ", title = "Expression of MMP13")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/MMP13.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_MMP13.csv")
```

#### CD4
```{r}
counts <- counts(dds['ENSG00000010610.9',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts))  + geom_jitter(width = 0.1) + aes(color= group) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none")
q <- q + labs(x = "Stage", y = "Normalized Counts ", title = "Expression of CD4")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/CD4.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_CD4.csv")
```

#### CD25/ ILR2A
```{r}
counts <- counts(dds['ENSG00000134460.15',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_jitter(width = 0.1) + aes(color= group) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") 
q <- q + labs(x = "Stage", y = "Normalized Counts ", title = "Expression of CD25/ ILR2A")
q
```


```{r}
ggsave("~/Desktop/Elizabeth_Figures/CD25.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_CD25.csv")
```


#### MYC 
```{r}
counts <- counts(dds['ENSG00000136997.16',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_jitter(width = 0.1) + aes(color= group) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") 
q <- q + labs(x = "Stage", y = "Normalized Counts ", title = "Expression of MYC")
q
```


```{r}
ggsave("~/Desktop/Elizabeth_Figures/MYC.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_MYC.csv")
```


#### CXCR4
```{r}
counts <- counts(dds['ENSG00000121966.6',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_jitter(width = 0.1) + aes(color= group) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") 
q <- q + labs(x = "Stage", y = "Normalized Counts ", title = "Expression of CXCR4")
q
```


```{r}
ggsave("~/Desktop/Elizabeth_Figures/CXCR4.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_CXCR4.csv")
```


#Activin Levels will be defined based on INHBA expression: 
### 30th Percentile: Low 29078.526385
### Between 30th and 70th: Intermediate 
### 70th Percentile: High 226640.63598

Redo with metadata

```{r message= FALSE, warning= FALSE, echo=FALSE}
sample_meta_data <- read.csv("~/Desktop/Elizabeth_Figures/TCGA_meta_with_activin.csv")
sampleNames <- sample_meta_data$From_Original_Order
activin <- sample_meta_data$Activin_Level
sampleTable <- data.frame(sampleName = sampleNames,
                          condition = activin)
sampleTable$condition <- factor(sampleTable$condition)
dds <- DESeqDataSetFromMatrix(ovarian_counts, sampleTable, ~condition)
```


```{r message= FALSE, warning= FALSE, echo=FALSE}
dds <- estimateSizeFactors(dds)
idx <- rowSums(counts(dds, normalized=TRUE) >= 5 ) >= 3
dds <- dds[idx,]
```


```{r message= FALSE, warning= FALSE, echo=FALSE}
library(BiocParallel)
dds <- DESeq(dds, quiet=TRUE, parallel=TRUE, BPPARAM=MulticoreParam(3))
```

#Genes of Interest

#### INHA 
```{r}
counts <- counts(dds['ENSG00000123999.4', ], normalized = TRUE)
col = c(Low= "#B8DE29FF", Intermediate= "#20A387FF", High= "#453781FF")
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group)) + geom_jitter(width = 0.1) + aes(color= group) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") + scale_x_discrete(limits=c("Low","Intermediate","High"))
q <- q + labs(x = "Activin Levels", y = "Normalized Counts ", title = "Expression of INHBA")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/activin_INHA.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_activin_INHA.csv")
```

#### INHBA
```{r}
counts <- counts(dds['ENSG00000122641.10', ], normalized = TRUE)
col = c(High= "#453781FF", Intermediate= "#20A387FF", Low= "#B8DE29FF")
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group)) + geom_jitter(width = 0.1) + aes(color= group) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") + scale_x_discrete(limits=c("Low","Intermediate","High"))
q <- q + labs(x = "Activin Levels", y = "Normalized Counts ", title = "Expression of INHBA")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/activin_INHBA.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_activin_INHBA.csv")
```

#### ACVR2A
```{r}
counts <- counts(dds['ENSG00000121989.14', ], normalized = TRUE)
col = c(High= "#453781FF", Intermediate= "#20A387FF", Low= "#B8DE29FF")
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group)) + geom_jitter(width = 0.1) + aes(color= group) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") + scale_x_discrete(limits=c("Low","Intermediate","High"))
q <- q + labs(x = "Activin Levels", y = "Normalized Counts ", title = "Expression of ACVR2A")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/activin_ACVR2A.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_activin_ACVR2A.csv")
```

#### ACVR2B
```{r}
counts <- counts(dds['ENSG00000114739.13',], normalized = TRUE)
col = c(High= "#453781FF", Intermediate= "#20A387FF", Low= "#B8DE29FF")
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group)) + geom_jitter(width = 0.1) + aes(color= group) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") + scale_x_discrete(limits=c("Low","Intermediate","High")) 
q <- q + labs(x = "Activin Levels", y = "Normalized Counts ", title = "Expression of ACVR2B")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/activin_ACVR2B.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_activin_ACVR2B.csv")
```

#### FOXP3
```{r}
counts <- counts(dds['ENSG00000049768.14',], normalized = TRUE)
col = c(High= "#453781FF", Intermediate= "#20A387FF", Low= "#B8DE29FF")
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group)) + geom_jitter(width = 0.1) + aes(color= group) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") + scale_x_discrete(limits=c("Low","Intermediate","High"))
q <- q + labs(x = "Activin Levels", y = "Normalized Counts ", title = "Expression of FOXP3")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/activin_FOXP3.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_activin_FOXP3.csv")
```

#### INHBB
```{r}
counts <- counts(dds['ENSG00000163083.5',], normalized = TRUE)
col = c(High= "#453781FF", Intermediate= "#20A387FF", Low= "#B8DE29FF")
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group)) + geom_jitter(width = 0.1) + aes(color= group) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") + scale_x_discrete(limits=c("Low","Intermediate","High")) 
q <- q + labs(x = "Activin Levels", y = "Normalized Counts ", title = "Expression of INHBB")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/activin_INHBB.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_activin_INHBB.csv")
```

#### ACVR1B
```{r}
counts <- counts(dds['ENSG00000135503.12',], normalized = TRUE)
col = c(High= "#453781FF", Intermediate= "#20A387FF", Low= "#B8DE29FF")
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group)) + geom_jitter(width = 0.1) + aes(color= group) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") + scale_x_discrete(limits=c("Low","Intermediate","High")) 
q <- q + labs(x = "Activin Levels", y = "Normalized Counts ", title = "Expression of ACVR1B")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/activin_ACVR1B.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_activin_ACVR1B.csv")
```

#### ACVR1C
```{r}
counts <- counts(dds['ENSG00000123612.15',], normalized = TRUE)
col = c(High= "#453781FF", Intermediate= "#20A387FF", Low= "#B8DE29FF")
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group)) + geom_jitter(width = 0.1) + aes(color= group) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") + scale_x_discrete(limits=c("Low","Intermediate","High")) 
q <- q + labs(x = "Activin Levels", y = "Normalized Counts ", title = "Expression of ACVR1C")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/activin_ACVR1C.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_activin_ACVR1C.csv")
```

#### CD8A
```{r}
counts <- counts(dds['ENSG00000153563.15',], normalized = TRUE)
col = c(High= "#453781FF", Intermediate= "#20A387FF", Low= "#B8DE29FF")
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group)) + geom_jitter(width = 0.1) + aes(color= group) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") + scale_x_discrete(limits=c("Low","Intermediate","High")) 
q <- q + labs(x = "Activin Levels", y = "Normalized Counts ", title = "Expression of CD8A")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/activin_CD8A.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_activin_CD8A.csv")
```

#### CD3G
```{r}
counts <- counts(dds['ENSG00000160654.9',], normalized = TRUE)
col = c(High= "#453781FF", Intermediate= "#20A387FF", Low= "#B8DE29FF")
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group)) + geom_jitter(width = 0.1) + aes(color= group) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") + scale_x_discrete(limits=c("Low","Intermediate","High")) 
q <- q + labs(x = "Activin Levels", y = "Normalized Counts ", title = "Expression of CD3G")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/activin_CD3G.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_activin_CD3G.csv")
```

#### MMP3 
```{r}
counts <- counts(dds['ENSG00000149968.11',], normalized = TRUE)
col = c(High= "#453781FF", Intermediate= "#20A387FF", Low= "#B8DE29FF")
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group)) + geom_jitter(width = 0.1) + aes(color= group) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") + scale_x_discrete(limits=c("Low","Intermediate","High")) 
q <- q + labs(x = "Activin Levels", y = "Normalized Counts ", title = "Expression of MMP3")
q
```
```{r}
ggsave("~/Desktop/Elizabeth_Figures/activin_MMP3.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_activin_MMP3.csv")
```

#### MMP13
```{r}
counts <- counts(dds['ENSG00000137745.11',], normalized = TRUE)
col = c(High= "#453781FF", Intermediate= "#20A387FF", Low= "#B8DE29FF")
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group)) + geom_jitter(width = 0.1) + aes(color= group) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") + scale_x_discrete(limits=c("Low","Intermediate","High")) 
q <- q + labs(x = "Activin Levels", y = "Normalized Counts ", title = "Expression of MMP13")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/activin_MMP13.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_activin_MMP13.csv")
```

#### CD4
```{r}
counts <- counts(dds['ENSG00000010610.9',], normalized = TRUE)
col = c(High= "#453781FF", Intermediate= "#20A387FF", Low= "#B8DE29FF")
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group)) + geom_jitter(width = 0.1) + aes(color= group) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") + scale_x_discrete(limits=c("Low","Intermediate","High")) 
q <- q + labs(x = "Activin Levels", y = "Normalized Counts ", title = "Expression of CD4")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/activin_CD4.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_activin_CD4.csv")
```

#### CD25/ ILR2A
```{r}
counts <- counts(dds['ENSG00000134460.15',], normalized = TRUE)
col = c(High= "#453781FF", Intermediate= "#20A387FF", Low= "#B8DE29FF")
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group)) + geom_jitter(width = 0.1) + aes(color= group) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") + scale_x_discrete(limits=c("Low","Intermediate","High")) 
q <- q + labs(x = "Activin Levels", y = "Normalized Counts ", title = "Expression of CD25/ ILR2A")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/activin_CD25.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_activin_CD25.csv")
```


#### MYC 
```{r}
counts <- counts(dds['ENSG00000136997.16',], normalized = TRUE)
col = c(High= "#453781FF", Intermediate= "#20A387FF", Low= "#B8DE29FF")
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group)) + geom_jitter(width = 0.1) + aes(color= group) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") + scale_x_discrete(limits=c("Low","Intermediate","High")) 
q <- q + labs(x = "Activin Levels", y = "Normalized Counts ", title = "Expression of MYC")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/activin_MYC.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_activin_MYC.csv")
```


#### CXCR4
```{r}
counts <- counts(dds['ENSG00000121966.6', ], normalized = TRUE)
col = c(High= "#453781FF", Intermediate= "#20A387FF", Low= "#B8DE29FF")
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group)) + geom_jitter(width = 0.1) + aes(color= group) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + theme(text = element_text(size = 13)) + theme(axis.text.y = element_text(size = 17)) + theme(legend.position="none") + scale_x_discrete(limits=c("Low","Intermediate","High")) 
q <- q + labs(x = "Activin Levels", y = "Normalized Counts ", title = "Expression of CXCR4")
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Figures/activin_CXCR4.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Figures/counts_activin_CXCR4.csv")
```

#to make your own meta data from recount projects 
```{r}
write.csv(age,"~/Desktop/Elizabeth_Figures/age.csv")
write.csv(case_id,"~/Desktop/Elizabeth_Figures/case_id.csv")
write.csv(case_id_gdc,"~/Desktop/Elizabeth_Figures/case_id_gdc.csv")
write.csv(ethnicity,"~/Desktop/Elizabeth_Figures/ethnicity.csv")
write.csv(external_id,"~/Desktop/Elizabeth_Figures/external_id.csv")
write.csv(lymphocyte,"~/Desktop/Elizabeth_Figures/lymphocyte.csv")
write.csv(monocyte,"~/Desktop/Elizabeth_Figures/monocyte.csv")
write.csv(neutrophil,"~/Desktop/Elizabeth_Figures/neutrophil.csv")
write.csv(normal_cells,"~/Desktop/Elizabeth_Figures/normal_cells.csv")
write.csv(project_names,"~/Desktop/Elizabeth_Figures/project_names.csv")
write.csv(race,"~/Desktop/Elizabeth_Figures/race.csv")
write.csv(stage,"~/Desktop/Elizabeth_Figures/stage.csv")
write.csv(tcga_barcodes,"~/Desktop/Elizabeth_Figures/tcga_barcodes.csv")
```
#these match to what is pulled from TCGA 
