---
title: "Activin_TCGA"
output: html_document
date: "2022-10-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("recount3")
ovarian_recount3 <- recount3::create_rse_manual(
  project = "OV",
  project_home = "data_sources/tcga",
  organism = "human",
  annotation = "gencode_v26",
  type = "gene"
)
```

```{r}
ovarian_counts <- ovarian_recount3@assays@data@listData$raw_counts
write.csv(ovarian_counts, "~/Desktop/rawcounts.csv")
```

```{r}
#necessary meta data 
tcga_barcodes <- ovarian_recount3@colData@listData[["tcga.tcga_barcode"]]
project_names <- ovarian_recount3@colData@listData[["tcga.gdc_cases.project.name"]]
write.csv(tcga_barcodes, "~/Desktop/barcodes.csv")
write.csv(project_names, "~/Desktop/project_names.csv")
```

```{r}
case_id <- ovarian_recount3@colData@listData[["tcga.gdc_cases.case_id"]]
write.csv(case_id, "~/Desktop/case_id.csv")
```


before this make the meta information from TCGA's website as well as the information from above 

```{r message= FALSE, warning= FALSE, echo=FALSE}
library(tximport)
library(GenomicFeatures)
library(TxDb.Hsapiens.UCSC.hg19.knownGene)
library(DESeq2)
library(tibble)
library(ggplot2)
```

```{r message= FALSE, warning= FALSE, echo=FALSE}
sample_meta_data <- read.csv("~/Desktop/Elizabeth_Paper_Activin/TCGA_meta_with_activin.csv")
sampleNames <- sample_meta_data$From_Original_Order
figo_stage <- sample_meta_data$figo_stage

sampleTable <- data.frame(sampleName = sampleNames,
                          condition = figo_stage)
sampleTable$condition <- factor(sampleTable$condition)
dds <- DESeqDataSetFromMatrix(ovarian_counts, sampleTable, ~condition)
```


```{r message= FALSE, warning= FALSE, echo=FALSE}
dds <- estimateSizeFactors(dds)
idx <- rowSums(counts(dds, normalized=TRUE) >= 5 ) >= 3
dds <- dds[idx,]
```


```{r message= FALSE, warning= FALSE, echo=FALSE}
dds <- DESeq(dds)
```


```{r message= FALSE, warning= FALSE, echo=FALSE}
res <- results(dds)
```

```{r}
res
```

```{r}
resOrdered <- res[order(res$pvalue),]
summary(res)
```

```{r}
res05 <- results(dds, alpha=0.05)
summary(res05)
```

```{r}
plotMA(res, ylim= c(-2,2))
```

#Analysis of Genes of Interest by Stage 
#### INHA 
```{r}
col <- c("Stage I" = "#fde725", "Stage II" = "#c8e020" ,"Stage III"= "#5ec962", "StageIV"= "#35b779")
```


```{r}
counts <- counts(dds['ENSG00000123999.4', ], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group))
q <- q + labs(y = "Normalized Counts", title = "Expression of INHA") + theme(legend.position= "none") + labs(x= "Stage") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Stage I","Stage II","Stage III", "Stage IV")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/INHA.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/counts_INHA.csv")
```

#### INHBA
```{r}
counts <- counts(dds['ENSG00000122641.10' , ], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group))
q <- q + labs(y = "Normalized Counts", title = "Expression of INHBA") + theme(legend.position= "none") + labs(x= "Stage") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Stage I","Stage II","Stage III", "Stage IV")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/INHBA.tiff", plot = last_plot())
write.csv(counts, "~/DesktopElizabeth_Paper_Activin/TCGA/By_Stage/counts_INHBA.csv")
```

#### ACVR2A
```{r}
counts <- counts(dds['ENSG00000121989.14',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group))
q <- q + labs(y = "Normalized Counts", title = "Expression of ACVR2A") + theme(legend.position= "none") + labs(x= "Stage") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Stage I","Stage II","Stage III", "Stage IV")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/ACVR2A.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/counts_ACVR2A.csv")
```

#### ACVR2B
```{r}
counts <- counts(dds['ENSG00000114739.13',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- q + labs(y = "Normalized Counts", title = "Expression of ACVR2B") + theme(legend.position= "none") + labs(x= "Stage") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Stage I","Stage II","Stage III", "Stage IV")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/ACVR2B.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/counts_ACVR2B.csv")
```

#### FOXP3
```{r}
counts <- counts(dds['ENSG00000049768.14',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- q + labs(y = "Normalized Counts", title = "Expression of FOXP3") + theme(legend.position= "none") + labs(x= "Stage") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Stage I","Stage II","Stage III", "Stage IV")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/FOXP3.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/counts_FOXP3.csv")
```

#### INHBB
```{r}
counts <- counts(dds['ENSG00000163083.5',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- q + labs(y = "Normalized Counts", title = "Expression of INHBB") + theme(legend.position= "none") + labs(x= "Stage") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Stage I","Stage II","Stage III", "Stage IV")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/INHBB.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/counts_INHBB.csv")
```

#### ACVR1B
```{r}
counts <- counts(dds['ENSG00000135503.12',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- q + labs(y = "Normalized Counts", title = "Expression of ACVR1B") + theme(legend.position= "none") + labs(x= "Stage") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Stage I","Stage II","Stage III", "Stage IV")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/ACVR1B.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/counts_ACVR1B.csv")
```

#### ACVR1C
```{r}
counts <- counts(dds['ENSG00000123612.15',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- q + labs(y = "Normalized Counts", title = "Expression of ACVR1C") + theme(legend.position= "none") + labs(x= "Stage") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Stage I","Stage II","Stage III", "Stage IV")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```

```{r}
ggsave("~/DesktopElizabeth_Paper_Activin/TCGA/By_Stage/ACVR1C.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/counts_ACVR1C.csv")
```

#### CD8A
```{r}
counts <- counts(dds['ENSG00000153563.15',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- q + labs(y = "Normalized Counts", title = "Expression of CD8A") + theme(legend.position= "none") + labs(x= "Stage") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Stage I","Stage II","Stage III", "Stage IV")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```

```{r}
ggsave("~/DesktopElizabeth_Paper_Activin/TCGA/By_Stage/CD8A.tiff", plot = last_plot())
write.csv(counts, "~/DesktopElizabeth_Paper_Activin/TCGA/By_Stage/countsCD8A.csv")
```

#### CD3G
```{r}
counts <- counts(dds['ENSG00000160654.9',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- q + labs(y = "Normalized Counts", title = "Expression of CD3G") + theme(legend.position= "none") + labs(x= "Stage") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Stage I","Stage II","Stage III", "Stage IV")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/CD3G.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/counts_CD3G.csv")
```

#### MMP3 
```{r}
counts <- counts(dds['ENSG00000149968.11',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- q + labs(y = "Normalized Counts", title = "Expression of MMP3") + theme(legend.position= "none") + labs(x= "Stage") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Stage I","Stage II","Stage III", "Stage IV")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/MMP3.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage//counts_MMP3.csv")
```

#### MMP13
```{r}
counts <- counts(dds['ENSG00000137745.11',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- q + labs(y = "Normalized Counts", title = "Expression of MMP13") + theme(legend.position= "none") + labs(x= "Stage") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Stage I","Stage II","Stage III", "Stage IV")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/MMP13.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/counts_MMP13.csv")
```

#### CD4
```{r}
counts <- counts(dds['ENSG00000010610.9',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- q + labs(y = "Normalized Counts", title = "Expression of CD4") + theme(legend.position= "none") + labs(x= "Stage") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Stage I","Stage II","Stage III", "Stage IV")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/CD4.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/counts_CD4.csv")
```

#### CD25/ ILR2A
```{r}
counts <- counts(dds['ENSG00000134460.15',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- q + labs(y = "Normalized Counts", title = "Expression of CD25") + theme(legend.position= "none") + labs(x= "Stage") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Stage I","Stage II","Stage III", "Stage IV")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```


```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/CD25.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/counts_CD25.csv")
```


#### MYC 
```{r}
counts <- counts(dds['ENSG00000136997.16',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- q + labs(y = "Normalized Counts", title = "Expression of MYC") + theme(legend.position= "none") + labs(x= "Stage") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Stage I","Stage II","Stage III", "Stage IV")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```


```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/MYC.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/counts_MYC.csv")
```


#### CXCR4
```{r}
counts <- counts(dds['ENSG00000121966.6',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sampleTable$condition)
m <- as_tibble(m)
q <- q + labs(y = "Normalized Counts", title = "Expression of CXCR4") + theme(legend.position= "none") + labs(x= "Stage") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Stage I","Stage II","Stage III", "Stage IV")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
q
```


```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/CXCR4.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Stage/counts_CXCR4.csv")
```


#Activin Levels will be defined based on INHBA expression: 
### 30th Percentile: Low 29078.526385
### Between 30th and 70th: Intermediate 
### 70th Percentile: High 226640.63598

Redo with metadata

```{r message= FALSE, warning= FALSE, echo=FALSE}
sample_meta_data <- read.csv("~/Desktop/Elizabeth_Figures/Meta Data/TCGA_meta_with_activin.csv")
sampleNames <- sample_meta_data$From_Original_Order
activin <- sample_meta_data$Activin_Level
sampleTable <- data.frame(sampleName = sampleNames,
                          condition = activin)
sampleTable$condition <- factor(sampleTable$condition)
dds <- DESeqDataSetFromMatrix(ovarian_counts, sampleTable, ~condition)
```


```{r message= FALSE, warning= FALSE, echo=FALSE}
dds <- estimateSizeFactors(dds)
idx <- rowSums(counts(dds, normalized=TRUE) >= 5 ) >= 3
dds <- dds[idx,]
```


```{r message= FALSE, warning= FALSE, echo=FALSE}
dds <- DESeq(dds)
```

```{r message= FALSE, warning= FALSE, echo=FALSE}
res <- results(dds,  contrast=c("condition","High","Low"))
res_2 <- results(dds,  contrast=c("condition","Low","High"))

write.csv(res, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/results_DeSeq2_condition_high_low.csv")

write.csv(res_2, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/results_DeSeq2_condition_low_high.csv")
```


#Genes of Interest

#### INHA 
```{r}
counts <- counts(dds['ENSG00000123999.4', ], normalized = TRUE)
col = c(Low= "#fde725", Intermediate= "#90d743", High= "#35b779")
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group))
q <- q + labs(y = "Normalized Counts", title = "Expression of INHA") + theme(legend.position= "none") + labs(x= "Activin (INHBA) Quantification") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Low","Intermediate","High")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/activin_INHA.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/counts_activin_INHA.csv")
```

#### INHBA
```{r}
counts <- counts(dds['ENSG00000122641.10', ], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group))
q <- q + labs(y = "Normalized Counts", title = "Expression of INHBA") + theme(legend.position= "none") + labs(x= "Activin (INHBA) Quantification") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Low","Intermediate","High")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/activin_INHBA.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/counts_activin_INHBA.csv")
```

#### ACVR2A
```{r}
counts <- counts(dds['ENSG00000121989.14', ], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group))
q <- q + labs(y = "Normalized Counts", title = "Expression of ACVR2A") + theme(legend.position= "none") + labs(x= "Activin (INHBA) Quantification") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Low","Intermediate","High")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/activin_ACVR2A.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/counts_activin_ACVR2A.csv")
```

#### ACVR2B
```{r}
counts <- counts(dds['ENSG00000114739.13',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group))
q <- q + labs(y = "Normalized Counts", title = "Expression of ACVR2B") + theme(legend.position= "none") + labs(x= "Activin (INHBA) Quantification") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Low","Intermediate","High")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/activin_ACVR2B.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/counts_activin_ACVR2B.csv")
```

#### FOXP3
```{r}
counts <- counts(dds['ENSG00000049768.14',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group))
q <- q + labs(y = "Normalized Counts", title = "Expression of FOXP3") + theme(legend.position= "none") + labs(x= "Activin (INHBA) Quantification") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Low","Intermediate","High")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/activin_FOXP3.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/counts_activin_FOXP3.csv")
```

#### INHBB
```{r}
counts <- counts(dds['ENSG00000163083.5',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group))
q <- q + labs(y = "Normalized Counts", title = "Expression of INHBB") + theme(legend.position= "none") + labs(x= "Activin (INHBA) Quantification") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Low","Intermediate","High")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/activin_INHBB.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/counts_activin_INHBB.csv")
```

#### ACVR1B
```{r}
counts <- counts(dds['ENSG00000135503.12',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group))
q <- q + labs(y = "Normalized Counts", title = "Expression of ACVR1B") + theme(legend.position= "none") + labs(x= "Activin (INHBA) Quantification") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Low","Intermediate","High")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/activin_ACVR1B.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/counts_activin_ACVR1B.csv")
```

#### ACVR1C
```{r}
counts <- counts(dds['ENSG00000123612.15',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group))
q <- q + labs(y = "Normalized Counts", title = "Expression of ACVR1C") + theme(legend.position= "none") + labs(x= "Activin (INHBA) Quantification") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Low","Intermediate","High")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/activin_ACVR1C.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/counts_activin_ACVR1C.csv")
```

#### CD8A
```{r}
counts <- counts(dds['ENSG00000153563.15',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group))
q <- q + labs(y = "Normalized Counts", title = "Expression of CD8A") + theme(legend.position= "none") + labs(x= "Activin (INHBA) Quantification") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Low","Intermediate","High")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/activin_CD8A.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/counts_activin_CD8A.csv")
```

#### CD3G
```{r}
counts <- counts(dds['ENSG00000160654.9',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group))
q <- q + labs(y = "Normalized Counts", title = "Expression of CD3G") + theme(legend.position= "none") + labs(x= "Activin (INHBA) Quantification") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Low","Intermediate","High")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/activin_CD3G.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/counts_activin_CD3G.csv")
```

#### MMP3 
```{r}
counts <- counts(dds['ENSG00000149968.11',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group))
q <- q + labs(y = "Normalized Counts", title = "Expression of MMP3") + theme(legend.position= "none") + labs(x= "Activin (INHBA) Quantification") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Low","Intermediate","High")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/activin_MMP3.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/counts_activin_MMP3.csv")
```

#### MMP13
```{r}
counts <- counts(dds['ENSG00000137745.11',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group))
q <- q + labs(y = "Normalized Counts", title = "Expression of MMP13") + theme(legend.position= "none") + labs(x= "Activin (INHBA) Quantification") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Low","Intermediate","High")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/activin_MMP13.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/counts_activin_MMP13.csv")
```

#### CD4
```{r}
counts <- counts(dds['ENSG00000010610.9',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group))
q <- q + labs(y = "Normalized Counts", title = "Expression of CD4") + theme(legend.position= "none") + labs(x= "Activin (INHBA) Quantification") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Low","Intermediate","High")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/activin_CD4.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/counts_activin_CD4.csv")
```

#### CD25/ ILR2A
```{r}
counts <- counts(dds['ENSG00000134460.15',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group))
q <- q + labs(y = "Normalized Counts", title = "Expression of CD25") + theme(legend.position= "none") + labs(x= "Activin (INHBA) Quantification") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Low","Intermediate","High")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/activin_CD25.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/counts_activin_CD25.csv")
```


#### MYC 
```{r}
counts <- counts(dds['ENSG00000136997.16',], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group))
q <- q + labs(y = "Normalized Counts", title = "Expression of MYC") + theme(legend.position= "none") + labs(x= "Activin (INHBA) Quantification") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Low","Intermediate","High")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/activin_MYC.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/counts_activin_MYC.csv")
```


#### CXCR4
```{r}
counts <- counts(dds['ENSG00000121966.6', ], normalized = TRUE)
m <- list(counts = as.numeric(counts), group= sample_meta_data$Activin_Level)
m <- as_tibble(m)
q <- ggplot(m, aes(group, counts)) + geom_boxplot(aes(fill= group))
q <- q + labs(y = "Normalized Counts", title = "Expression of cxcr4") + theme(legend.position= "none") + labs(x= "Activin (INHBA) Quantification") + theme(text = element_text(size = 20)) + theme(panel.background = element_blank(), panel.grid.major= element_line()) + theme(axis.line = element_line(colour = "black")) + scale_x_discrete(limits=c("Low","Intermediate","High")) + scale_fill_manual(values = alpha(col,.3)) +scale_color_manual(values = alpha(col, 1.0)) + aes(color= group)
q
```

```{r}
ggsave("~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/activin_CXCR4.tiff", plot = last_plot())
write.csv(counts, "~/Desktop/Elizabeth_Paper_Activin/TCGA/By_Activin/counts_activin_CXCR4.csv")
```

